Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-03-20 paper/paper.qmd
resolving git issues

\section*{Conclusion}
The results of the assumption tests (Shapiro-Wilk, Mauchly's, and Levene's) were used to determine whether the assumptions of normality, sphericity, and homogeneity of variance were met. If any assumptions were violated, appropriate corrections or alternative methods were considered before proceeding with the repeated measures ANOVA.
```{r}
#| label: tbl-model1
#| tbl-cap: "Summary of Age Groups"
#| echo: false
#| warning: false
#| message: false

# Load necessary libraries
library(tidyverse)
library(ggplot2)
library(car)
library(ez)

# Assuming the dataset is loaded into a data frame called `data`
# Convert necessary columns to factors
clean_data$Drug <- as.factor(clean_data$Drug)
clean_data$DosageLevel <- as.factor(clean_data$DosageLevel)
clean_data$Time <- as.factor(clean_data$Time)
clean_data$AgeGroup <- as.factor(clean_data$AgeGroup)

# Check for Normality
# We will use Shapiro-Wilk test for normality
shapiro_test <- clean_data %>%
  group_by(Drug, DosageLevel, Time) %>%
  summarise(statistic = shapiro.test(GameScore)$statistic,
            p.value = shapiro.test(GameScore)$p.value)

print(shapiro_test)

# Visual check for normality using Q-Q plots
ggplot(clean_data, aes(sample = GameScore)) +
  geom_qq() +
  geom_qq_line() +
  facet_grid(Drug ~ DosageLevel + Time) +
  theme_minimal() +
  ggtitle("Q-Q Plots for Normality Check")

# Check for Sphericity using Mauchly's Test
# We will use the `ezANOVA` function to check for sphericity
ez_model <- ezANOVA(
  data = clean_data,
  dv = .(GameScore),
  wid = .(Name),
  within = .(Time),
  between = .(Drug, DosageLevel),
  type = 3,
  detailed = TRUE
)

print(ez_model)

>>>>

\section*{Conclusion}
The results of the assumption tests (Shapiro-Wilk, Mauchly's, and Levene's) were used to determine whether the assumptions of normality, sphericity, and homogeneity of variance were met. If any assumptions were violated, appropriate corrections or alternative methods were considered before proceeding with the repeated measures ANOVA.
